---
title: "STAT433 - HW2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(nycflights13)
library(ggplot2)
```

1) How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
flights_cancled <- flights %>%
  filter(is.na(dep_time))

flights_cancled;nrow(flights_cancled)
```

The number of rows (flights) that are missing dep_time are 8,255. Since missing variables suchs as dep_time, dep_delay, and arr_time are about departure, we can assume that the rows represent the flights whose departure was cancled. 


2) Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
flights_tempt <- select(flights,
                        dep_time,
                        sched_dep_time)

mutate(flights_tempt,
       dep_time = ( 24 * 60 ) - ( (dep_time %/% 100) * 60 + (dep_time %% 100) ),
       sched_dep_time = ( 24 * 60 ) - ( (sched_dep_time %/% 100) * 60 + (sched_dep_time %% 100) )
)
```

```{r}
# This is dummy code
minute <- as.integer(flights[1,5]) %% 100
hour <- as.integer(flights[1,5]) %/% 100

time_remained <- (24*60) - ( (hour * 60) + minute);time_remained
```

3) Look at the number of cancelled flights per day. Is there a pattern? Is the proportion of cancelled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with `ggplot(aes(x= ,y=)) + geom_point()'
  
The number of cancelled flights per day:

```{r}
flights_cancled_tempt <- flights_cancled %>%
  group_by(day) %>%
  summarize(count = n())

flights_cancled_tempt %>%
  ggplot(mapping = aes(x = day , y= count)) + geom_point(aes(size = count))

```
It seems like the number of missing flights per day is at its peak at around 8. Therefore, we can assume that at 8th day of a month, the number of canceled flight is the highest.


github link: https://github.com/rlawlstjr544/STAT433_HW2


